Extending Camellia for Distributed Stiffness Matrix Determination in DPG

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
adding figs to camellia, adding plotting functions, data, figs to repo
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@99 36274a68-8941-4c93-80ef-affaed5139da

\documentclass{article}
\include{jessePreamble} % contains commonly used packages/defined functions
\date{}
\author{Jesse Chan and Nathan V. Roberts}
\title{Extending Camellia for Distributed Stiffness Matrix Determination in DPG}

@@

\subsubsection{Design Limitations: Where Amdahl's Law Might Come to Haunt Us}
Here, we note a few features of the present design that may become bottlenecks as we scale up to larger problems and larger numbers of MPI nodes.

@@

>>>>

\documentclass{article}
\newcommand{\oneFig}{.65}
\newcommand{\twoFig}{.42}
\newcommand{\fourFig}{.42}

\include{jessePreamble} % contains commonly used packages/defined functions
\date{}
\author{Jesse Chan and Nathan V. Roberts}
\title{Extending Camellia for Distributed Stiffness Matrix Determination in DPG}

@@

\subsubsection{Design Limitations: where Amdahl's law might come to haunt us}
Here, we note a few features of the present design that may become bottlenecks as we scale up to larger problems and larger numbers of MPI nodes.

@@

Describe experimental setup
\begin{figure}
\centering
\subfigure[Cyclic]{
\includegraphics[scale = \twoFig]{figs/cyclic.pdf}
}
\subfigure[HSFC]{
\includegraphics[scale = \twoFig]{figs/hsfc.pdf}
}
\end{figure}

\subsection{Weak scaling}

\begin{figure}
\centering
\subfigure[Global stiffness assembly]{
\includegraphics[scale = \twoFig]{figs/scalingFigs/weakScalingAssembly.pdf}
}
\subfigure[Local stiffness computation]{
\includegraphics[scale = \twoFig]{figs/scalingFigs/weakScalingLocal.pdf}
}
\end{figure}

\subsection{Strong scaling}
\begin{figure}
\centering
\subfigure[Global stiffness assembly]{
\includegraphics[scale = \twoFig]{figs/scalingFigs/hsfcStrongScalingAssembly.pdf}
}
\subfigure[Local stiffness computation]{
\includegraphics[scale = \twoFig]{figs/scalingFigs/hsfcStrongScalingLocal.pdf}
}
\caption{Strong scaling statistics for a HSFC (localized) partitioning of the mesh.}
\end{figure}

\begin{figure}
\centering
\subfigure[Global stiffness assembly]{
\includegraphics[scale = \twoFig]{figs/scalingFigs/cyclicStrongScalingAssembly.pdf}
}
\subfigure[Local stiffness computation]{
\includegraphics[scale = \twoFig]{figs/scalingFigs/cyclicStrongScalingLocal.pdf}
}
\caption{Strong scaling statistics for a cyclic (non-localized) partitioning of the mesh.}
\end{figure}

\subsection{Breakdown of time spent}
\begin{figure}
\centering
\subfigure[202 elements, 13343 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref0.pdf}
}
\subfigure[808 elements, 52137 dofs ]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref1.pdf}
}
\subfigure[3232 elements, 206081 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref2.pdf}
}
\subfigure[12928 elements, 819393 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref3.pdf}
}
\caption{Strong scaling statistics for a cyclic (non-localized) partitioning of the mesh.}
\end{figure}
